Packing Boxes with Score Constraints

### 2017-08-30 docs/main.tex
updated MIS

\subsection{Mate-Induced Structure}

@@

>>>>

\subsection{Mate-Induced Structure}
Now that we have a list of matched scores, we can now attempt to create an \textit{alternating cycle} which consists of an edge between scores that are mates, followed by an edge between scores that are matched. Therefore each score will either be preceded by a mate and followed by a match, or vice versa. The cycles are easily formed using the mate list and match list.

If the mate-induced structure consists of only one cycle, then the instance is instantly feasible. In this example we have two cycles, and so we must find a way to connect, or ``patch'', these two cycles together to create a single cycle.

@@

\subsection{FCA}%change this title
